---
output: 
  html_document: 
    #theme: null
    #highlight: null
    mathjax: null
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), '/www/About.html')) })

---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(OCSRiskCalculator)
outcomes <- get_outcomes()
evidence <- get_evidence()
```

This Web Application is a relative risk calculator for long-term risk of oral corticosteroid (OCS) use in patients with asthma.

The calculations are based on a single peer-reviewed publication by [Sullivan et al, ](http://dx.doi.org/10.1016/j.jaci.2017.04.009){target="_blank"}. This is a rigorous retrospective cohort study with a large sample size from the US. The calculations do not represent the entire body of evidence. We focused on a single high-quality work that could produce risk calculation according to the dose and history of OCS use.


### Regression coefficients:
Table below presents the logarithm of relative risks (log-RR) associated with each outcome. 

The interpretation of coefficients are as follows:

* Reference: not currently taking OCS, and not having any history of OCS use
* cur_ocs_low: Whether the individual is taking low-dose OCS
* cur_ocs_high: Whether the individual is taking low-dose OCS
* hist_ocs_low_years: Number of previous years where the patient was taking low-dose OCS
* hist_ocs_high_years:  Number of previous years where the patient was taking high-dose OCS

```{r echo=FALSE}
df <- t(as.data.frame(evidence$ocs_coefficients))
o <- which(outcomes==rownames(df))
df <- df[o,]
rownames(df) <- names(outcomes)

kable(df)
```

In mapping these coefficients to person characteristics, the following simplified assumption was made: one question is asked about whether the person has been taking low-dose or high-dose OCS, which is applied both to current and past use. This is because remembering the nuances of OCS use over the years might be fraught with inaccuracy.


### Calculating rerlative risk

The equation for calculating RR is

$$ RR = exp(\beta_0X_0+\beta_1X_1+\beta_2X_2+\beta_3X_3) $$
where indices 0-3 refer to the four exposure variables as in the table above.



### Baseline risk
Estimating the baseline risk of events for the patient is out of the scope of this web application. Instead, for specific outcomes, this web app let's the user indicate their own baseline risk as if they have never taken OCS (this is to be done after consultation with their care provider). The absolute risk increase is then applied given the relative risk.

The slider for baseline risk is pre-populated with the 10-year incidence of outcomes in the comparison group (those who did not take OCS) in the study  by Sullivan et al. This is only a suggested default value. If the user profile is significantly different from a typical patient in the comparison cohort of Sullivan et al' study, this risk estimate can be substantially biased.


### Contact us
Should you want to contact the creators of this web application to provide feedback, please reach out to info@naptia.com. 
